Defending Against Web Application Attacks: Approaches, Challenges and Implications \vspace{-1mm}

### 2016-07-29 docs/comments/comments.tex
work on comments 1 and 2 of R3, 2 of R1 and 1 of R2

@@

\noindent
{\bf Response:}
Initial note:
This is an interesting comment.
We need to mention that we did not intend to
compare the mechanisms with each other.
Our intention was to highlight that currently there
are many different testing setups and
environments for defenses that counter
similar attacks (see Subsection 6.1).\\

\noindent
Second note:
We also changed the caption of Table 1.\\

@@

\noindent
{\bf Response:}
Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
Lorem Ipsum. Lorem Ipsum".\\

@@

\noindent
{\bf Response:}
Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
Lorem Ipsum. Lorem Ipsum".\\

@@

\noindent
{\bf Response:}
Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
Lorem Ipsum. Lorem Ipsum. Lorem Ipsum. Lorem Ipsum.
Lorem Ipsum. Lorem Ipsum".\\

>>>>

\noindent
{\bf Response:}
This is a valid comment.
However,
in order to avoid penalizing recent research,
we have also included recent papers
even though they have been cited less than twenty times.

In addition,
to address the comments of the 2nd and the 3rd reviewer,
we have included six more mechanisms,
thus making our study more extended.
Notably,
one of the mechanisms is presented in a recent
paper with less than 20 citations.
This increases the number of such papers
incorporated in our study (6).\\

@@

\noindent
{\bf Response:}
This is an interesting comment.
We need to mention that we did not intend to
compare the mechanisms with each other
but to highlight factors that may hinder
the widespread deployment of protection mechanisms
(we state this early on in the
``Introduction" section).

Indeed,
the caption of Table 1 actually
started with the phrase ``comparison summary"
which is misleading.
To avoid any further misunderstandings
we have changed the caption of Table 1
to make clear that there
are many different testing setups and
environments for defenses that counter
similar attacks (see Subsection 6.1).\\

@@

@@

\noindent
{\bf Response:}
Indeed,
Cross Frame Scripting (\textsc{xfs}) attacks
are comprise a novel category worth mentioning.
We now refer to \textsc{xfs} attacks
at the end of Section 3 (``Exploitation Model").
We also provide a corresponding example.\\

@@

\noindent
{\bf Response:}
We have updated Section 3 (``Exploitation Model")
to include {\sc dom}-based {\sc xss} attacks
as a the third basic category of {\sc xss}
attacks.\\

### 2016-07-29 docs/paper/questioning.tex
work on comments 1 and 2 of R3, 2 of R1 and 1 of R2

Cross-site scripting attacks fall into two categories, {\it non-persistent}
(also known as \emph{reflected}) {\sc xss}
and {\it persistent} (also known as \emph{stored}) {\sc xss}.
Non-persistent {\sc xss} attacks take place when the
data provided by a user is processed on-the-fly
by server-side application logic and ends up without proper sanitization
into a dynamically generated response ({\sc p-xss} 7, {\sc n-xss} 2)
that is eventually rendered by the user's browser.
Thus, in a non-persistent {\sc xss} attack, the injected code
is not saved on the server, but immediately becomes part of the
content that is sent back to a user.
In persistent {\sc xss} attacks, on the other hand,
malicious code is permanently stored on the server ({\sc p-xss} 5).
The injected code residing at server-side then re-enters the
application's execution flow and becomes part of the content that is
eventually sent to the user as part of a future response.

@@

@@

Vogt et al.~\cite{VFJKKV07} have developed a tainting scheme
that follows a different approach. In contrast to the above
schemes, which operate on the server-side, their technique tracks sensitive
information at the client-side (Point {\sc ub}). This is a form of
positive data flow tracking, where tagged data is considered to be
legitimate. Their scheme detects JavaScript-driven {\sc xss} attacks
by ensuring that a script can send sensitive user data only to the
site from which it came from.
Stock et al.~\cite{SLMS14} propose a scheme that also operates
in the browser (Point {\sc ub}). The scheme focuses on the detection of
{\sc dom}-based {\sc xss} attacks. In such an attack, the malicious
payload is executed as a result of the modification of the {\sc dom}
environment so that the client-side code runs in an unanticipated
manner, even if the {\sc http} response that triggers the injection
seems legitimate. This scheme is different from the previous one
because it marks and observes data that are considered harmful.
Specifically, it employs a taint-enhanced JavaScript engine that
tracks the flow of attacker-controlled data. To detect potential
attacks, the scheme uses {\sc html} and JavaScript parsers that can
identify the generation of code coming from tainted data.

>>>>

Cross-site scripting
attacks fall into \hlc[yellow]{three} categories,
{\it non-persistent}
(also known as \emph{reflected}) {\sc xss},
{\it persistent} (also known as \emph{stored}) {\sc xss}
\hlc[yellow]{and {\sc dom}\textit{-based} \textsc{xss}.}
Non-persistent {\sc xss} attacks take place when the
data provided by a user is processed on-the-fly
by server-side application logic and ends up without proper sanitization
into a dynamically generated response ({\sc p-xss} 7, {\sc n-xss} 2)
that is eventually rendered by the user's browser.
Thus, in a non-persistent {\sc xss} attack, the injected code
is not saved on the server, but immediately becomes part of the
content that is sent back to a user.
In persistent {\sc xss} attacks, on the other hand,
malicious code is permanently stored on the server ({\sc p-xss} 5).
The injected code residing at server-side then re-enters the
application's execution flow and becomes part of the content that is
eventually sent to the user as part of a future response.
\hlc[yellow]{In a {\sc dom}-based {\sc xss} attack,
the malicious payload is executed as a result of
the modification of the {\sc dom}
environment so that the client-side code runs
in an unanticipated manner,
even if the {\sc http} response that
triggers the injection seems legitimate.
Notably,
a {\sc dom}-based {\sc xss} attack
can follow a path of either a persistent {\sc xss}
attack or a non-persistent {\sc xss} attack.
Also,
it can be performed on-demand and purely client-side
across frames.}

@@

\hlc[yellow]{A Cross Frame Scripting (\textsc{xfs})
attack is a recent threat that combines
a malicious script with
an {\tt iframe} that loads a legitimate page in
an effort to steal data from a user.
Consider an attacker that lures
a user to navigate to a web page the attacker controls
via social engineering.
The attacker's page then loads JavaScript
and an HTML {\tt iframe} pointing to a legitimate site.
Once the user enters his or her
credentials into the legitimate site,
the malicious script records all keystrokes.
An {\sc xfs} attack can be also captured by our model
because the steps are pretty similar to the steps of
a non-persistent \textsc{xss} attack.}

@@

Vogt et al.~\cite{VFJKKV07} have developed a tainting scheme
that follows a different approach. In contrast to the above
schemes, which operate on the server-side, their technique tracks sensitive
information at the client-side (Point {\sc ub}). This is a form of
positive data flow tracking, where tagged data is considered to be
legitimate. Their scheme detects JavaScript-driven {\sc xss} attacks
by ensuring that a script can send sensitive user data only to the
site from which it came from.
Stock et al.~\cite{SLMS14} propose a scheme that also operates
in the browser (Point {\sc ub}). The scheme focuses on the detection of
{\sc dom}-based {\sc xss} attacks.
This scheme is different from the previous one
because it marks and observes data that are considered harmful.
Specifically, it employs a taint-enhanced JavaScript engine that
tracks the flow of attacker-controlled data. To detect potential
attacks, the scheme uses {\sc html} and JavaScript parsers that can
identify the generation of code coming from tainted data.
